### 2020-04-13 reports/thesis/book.tex
Flowchart is png
Corrections
Corrections
CpEmAlgorithm does not plot estimated std
roc calculates area exactly
Recoded NullIid and included biweighted mean

\documentclass[12pt, a4paper, oneside]{memoir}
%oneside for soft copy
%twoside for hard final copy
\setlrmargins{4.3cm}{*}{*}
\checkandfixthelayout
%\documentclass[12pt, a4paper, oldfontcommands]{memoir}
%\documentclass[12pt, a4paper]{report}

@@

\let\footruleskip\undefined
\usepackage{fancyhdr}
\fancypagestyle{plain}{%
\fancyhf{}% clears all header and footer fields
\fancyhead[LE,RO]{\thepage}%
\renewcommand{\headrulewidth}{0pt}%
\renewcommand{\footrulewidth}{0pt}}

@@

@@

Parts of this thesis is anticipated to be published by the author:
\begin{itemize}
  \item\nobibliography*\bibentry{lo2019detection}
\end{itemize}

@@

This thesis is a contribution to real-time quality control in additive manufacturing.

@@

In Chapter \ref{chapter1}, x-ray computed tomography and additive manufacturing is reviewed. Sources of error were investigated and see how they were handled. In Chapter \ref{chapter2}, a test sample was additively manufactured and the chapter describes how experimental x-ray projections were obtained. Shading correction is explained here and it was used to remove sources of systematic error in the projections. In Chapter \ref{chapter3}, the compound Poisson distribution is studied so that it can be used to model the detection of x-rays. In Chapter \ref{chapter4}, the uncertainty in the projection was quantified using the variance and generalised linear models were used to predict it. In Chapter \ref{chapter5}, novel statistical techniques were developed and implemented to look for defects in the test sample in the face of uncertainty. This was done by comparing the experimental projection with a simulated projection and looking for any disagreement. The empirical null filter was used to cater for any model misspecification so that sensible conclusions were made. The thesis ends with an evaluation in Chapter \ref{chapter6}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.64\textwidth]{../figures/flowchart.pdf}
  \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection. This results in pixels being highlighted as positive for defects.}
  \label{fig:evaluation_flowchart}
\end{figure}

@@

Two angular projections were looked at in this thesis. The angles were selected by the engineers, in calibration with this experiment, so that all of the voids were visible in a single projection. Defect detection can be tough if a difficult projection angle was used. Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden at a particular projection angle. Another possible extension is to integrate \emph{aRTist} into the inference, for example, the simulated projection could be realigned to minimise the number of positives. This will help eliminate sources of error due to \emph{aRTist}. A problem with this suggestion is that aligning the simulated projection is a high dimensional problem \citep{brierley2018optimized}.

Voids in the order of millimetres were detectable using this method. Further work could include test samples made from materials such as titanium alloys (Ti-6Al-4V). This can be challenging because artefacts, such as streaks, can appear when using XCT for metal parts \citep{deman1998metal, nawaz2014metal}. Another problem is that because titanium products are created using a power-based method, the powder may become trapped \citep{brierley2018optimized} in designed voids. This results in voids appearing with less contrast in the projections, making it harder to detect.

This thesis is a contribution to real-time quality control for AM. A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt. By using fewer projections, quality control can be faster which advances the development and increases the scope of applications of AM.

>>>>

\documentclass[12pt, a4paper, twoside]{memoir}
%oneside for soft copy
%twoside for hard final copy
\setlrmargins{4.3cm}{*}{*}
\checkandfixthelayout
%\documentclass[12pt, a4paper, oldfontcommands]{memoir}
%\documentclass[12pt, a4paper]{report}

@@

%page number of odd page on new chapter
\let\footruleskip\undefined
\usepackage{fancyhdr}
\fancypagestyle{plain}{%
\fancyhf{}% clears all header and footer fields
\fancyhead[LE,RO]{\thepage}%
\renewcommand{\headrulewidth}{0pt}%
\renewcommand{\footrulewidth}{0pt}}
\aliaspagestyle{cleared}{plain} %page number of blank even

@@

%\includepdf[page={1,2,3,4}]{licence.pdf}

@@

@@

@@

In Chapter \ref{chapter1}, x-ray computed tomography and additive manufacturing is reviewed. Sources of error were investigated and it was discuused how they were handled. In Chapter \ref{chapter2}, a test sample was additively manufactured and the chapter describes how experimental x-ray projections were obtained. Shading correction is explained here and it was used to remove sources of systematic error in the projections. In Chapter \ref{chapter3}, the compound Poisson distribution is studied so that it can be used to model the detection of x-rays. In Chapter \ref{chapter4}, the uncertainty in the projection was quantified using the variance and generalised linear models were used to predict it. In Chapter \ref{chapter5}, novel statistical techniques were developed and implemented to look for defects in the test sample in the face of uncertainty. This was done by comparing the experimental projection with a simulated projection and looking for any disagreement. The empirical null filter was used to cater for any model misspecification so that sensible conclusions were made. The thesis ends with an evaluation in Chapter \ref{chapter6}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.64\textwidth]{../figures/flowchart.png}
  \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection. This results in pixels being highlighted as positive for defects.}
  \label{fig:evaluation_flowchart}
\end{figure}

@@

The main statistical novelty was extending the empirical null \citep{efron2004large} to a filter where it can be applied to images. This has been implemented in \emph{ImageJ} \citep{abramoff2004image, schneider2012nih, perez2013image}. A by-product is the empirical null mean, which is effectively the mode filter, which can be used to smooth images.

Two angular projections were looked at in this thesis. The angles were selected by the engineers, in calibration with this experiment, so that all of the voids were visible in a single projection. Defect detection can be tough if a difficult projection angle was used. This experiment could be improved by analysing more angular projections independently to pick up voids which may be hidden at a particular projection angle. Another possible extension is to integrate \emph{aRTist} into the inference, for example, the simulated projection could be realigned to minimise the number of positives. This will help eliminate sources of error due to \emph{aRTist}. A problem with this suggestion is that aligning the simulated projection is a high dimensional problem \citep{brierley2018optimized}.

Voids in the order of millimetres were detectable using this method. Further work could include test samples made from materials such as titanium alloys (Ti-6Al-4V). This can be challenging because artefacts, such as streaks, can appear when using XCT for metal parts \citep{deman1998metal, nawaz2014metal}. Another problem is that because titanium products are created using a power-based method, the powder may become trapped \citep{brierley2018optimized} in designed voids. This results in voids appearing with less contrast in the projections, making it harder to detect. Different types of challenging defects could be investigated. For example, the orientation of cracks can affect the detectability of it \citep{wooldridge1997demonstrating}.

This thesis is a contribution to real-time quality control for AM and perhaps inverse problems in imaging \citep{bertero1998introduction} and robust statistics. A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt. This could be competitive with other converyor belt inspection methods, for example \cite{warnett2016towards}, by using less projections and hopefully less computational time. By using fewer projections, quality control can be faster which advances the development and increases the scope of applications of AM.
